An excess of positive results: Comparing the standard Psychology literature with Registered Reports

### 2021-02-18 submission2/positive_results_SRs_RRs_revision1.Rmd
Updated revised manuscript

Since the 1950s, scientists have repeatedly noted a suspiciously high "success" rate in Psychology:
Studying 362 empirical articles published in four Psychology journals in 1955/56, @Sterling1959 found that $97.28\%$ of studies using significance tests rejected the null hypothesis. 
A later replication of this study reported $95.56\%$ statistically significant results in articles from 1986/87 [@Sterling1995]. 
Similarly, a seminal study by @Fanelli2010 compared the literatures of 20 disciplines and found that $91.5\%$ of papers published in Psychology reported support for their first hypothesis, the highest estimate of all disciplines in the study. 
For these percentages to be a realistic representation of the research psychologists conduct, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed $90\%$. 
Put differently, nearly all predictions researchers make must be correct, and either the studied effects or the used samples (given the same design) must consistently be very large.
These two assumptions appear highly implausible a priori, and available evidence on average statistical power in the literature shows that at least one does not hold [e.g., @Szucs2017].

@@

Some have argued that selecting for positive results is defensible$\,$---$\,$desirable, even$\,$---$\,$because it weeds out low-quality research that would only pollute the literature [e.g., @Cleophas1999]. 
If most negative results that are currently missing from the literature are indeed due to immature ideas or poor methods, a literature that selects studies based on *quality* instead of results should contain a similar proportion of positive results as the current one. 
How many positive and negative results would such an unbiased literature contain in reality? 
We investigated this question by comparing the rate of positive results in the Psychology literature to studies published in a new format designed to minimise publication bias and QRPs: Registered Reports.

@@

## The current study
The goal of our study was to test if Registered Reports in Psychology have a lower positive result rate than articles published in the traditional way (henceforth "standard reports", SRs), and to estimate the size of this potential difference. 
Because the standards for research quality in Registered Reports are at least equal to ordinary peer review, and the statistical power requirements may exceed those in the standard literature [@Maxwell2004; @Szucs2017], such a difference would be unlikely to be due to "failed" studies or false negatives.
Should the positive result rate in Registered Reports be much lower than in the standard literature, it might then indicate that publication bias is not a desirable filter for poorly conducted studies, and that we ought to worry about high-quality negative results we are missing because of it.

@@

The sample size of standard reports was pre-specifided to replicate Fanelli's [-@Fanelli2010] ($n = 150$) since it matched the maximum number of available Registered Reports ($n = 151$, see below) and piloting indicated that the required coding time would just fit our resource constraints.
Standard reports were selected by searching the 633 journals listed under "Psychiatry/Psychology" in the Essential Science Indicators database for papers published between 2013 and 2018 that contained the phrase "test$^\ast$ the hypothes$^\ast$" in title, abstract, or keywords.
We then randomly selected 150 papers from the 1919 papers that resulted from this search. Excluded papers were replaced by resampling twice (this decision was not preregistered), which led to accidental oversampling and a final sample size of 152 (see Fig.\ \@ref(fig:sampling)).

@@

In Registered Reports, we coded the first *preregistered* hypothesis, thus excluding unregistered pilot studies. 
Coding disagreements between "full" and "partial" support were deemed minor since they would not affect the final results. 
Thus, only disagreements affecting the binary support (full or partial) vs no support classification were treated as major and resolved through discussion.
MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code ($`r sum(included$coded_by_AS & included$is_RR==1)`$ RRs and $`r sum(included$coded_by_AS & included$is_RR==0)`$ SRs). 
Only `r support.disagreement.major` disagreements were major (Cohen's kappa = `r printp(kappa.support)`) and subsequently resolved by discussion; `r support.disagreement.minor` were minor (disagreement between "support" and "partial support"). 
We overturned the preregistered plan that AS would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
Coders were not blind to condition (Registered Report vs standard report) because access to the full text was often necessary, the content of which would have made most Registered Reports clearly identifiable.

@@

We would accept our hypothesis that Registered Reports have a lower positive result rate than standard reports if the observed difference between Registered Reports and standard reports was significantly smaller than 0 *and* not statistically equivalent to a range from $-6\%$ to $+6\%$ (both at $\alpha = 5\%$).

@@

## Exploratory analyses
For ease of communication we will refer to papers that were classified as close replications of previously published work as "replications" and to all other studies as "original", even though the latter include some conceptual replications and internal replications (as explained above).
As expected, replications were much more common among Registered Reports ($`r n.rep.RR` / `r n.RR` = `r printnum(prop.rep.RR*100)`\%$) than standard reports ($`r n.rep.SR` / `r n.SR` = `r printnum(prop.rep.SR*100)`\%$), and replication Registered Reports had a descriptively lower positive result rate than original Registered Reports (see Table 1).
However, this finding fails to explain the main result described above:
When analysing only original papers, the difference between the positive result rates of Registered Reports and standard reports, $`r printnum((prop.orig.support.RR-prop.orig.support.SR)*100)`\%$, was still significantly different from 0 ($\chi^2(`r origproptest$parameter`) = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(abs(reptost$TOST_z1), abs(reptost$TOST_z2)))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.

@@

## Limitations
Our study was not an experiment$\,$---$\,$hypotheses, authors, and editors were not randomly assigned to each publication format$\,$---$\,$and thus precludes strong causal inferences.
As discussed above, it seems highly plausible that Registered Reports reduce publication bias and QRPs, which in turn reduces the positive result rate. 
Yet we neither know exactly how effective Registered Reports are at reducing bias, nor how large the effect on positive results would be in the absence of potential confounds. 
One such confound, as just discussed, could be that Registered Reports may be used for particularly risky hypotheses.
Another confound could be that the format attracts particularly conscientious authors who try to minimise the risk of inflated error rates regardless of the report format they use. 
This would lead to less bias in the Registered-Reports literature even if the format's safeguards against certain QRPs were actually ineffective.

>>>>

Since the 1950s, scientists have repeatedly noted a suspiciously high "success" rate in Psychology:
Studying 362 empirical articles published in four Psychology journals in 1955/56, @Sterling1959 found that $97.28\%$ of studies using significance tests rejected the null hypothesis. 
A later replication of this study reported $95.56\%$ statistically significant results in articles from 1986/87 [@Sterling1995]. 
Similarly, a seminal study by @Fanelli2010 analysed authors' verbal conclusions in hypothesis-testing papers sampled from the literatures of 20 disciplines and found that $91.5\%$ of papers published in Psychology claimed support for their first hypothesis$\,$---$\,$the highest estimate of all disciplines in the study. 
For these percentages to be a realistic representation of the research psychologists conduct, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed $90\%$. 
Put differently, nearly all predictions researchers make must be correct, and either the studied effects or the used samples (given the same design) must consistently be very large.
These two assumptions appear highly implausible a priori, and available evidence on average statistical power in the literature shows that at least one does not hold [e.g., @Szucs2017].

@@

Some have argued that negative results are often uninformative or the result of low-quality research and should not be published at the same rate as positive results to avoid cluttering the literature [e.g., @Cleophas1999; @Mitchell2014; @Baumeister2016]. 
If most negative results that are currently missing from the literature are indeed due to immature ideas or poor methods, a literature that selects studies based on *quality* instead of results should contain a similar proportion of positive results as the current one. 
How many positive and negative results would such an unbiased literature contain in reality? 
We investigated this question by comparing the rate of positive results in the Psychology literature to studies published in a new format designed to minimise publication bias and QRPs: Registered Reports.

@@

## The current study
The goal of our study was to test if Registered Reports in Psychology have a lower positive result rate than articles published in the traditional way (henceforth "standard reports", SRs), and to estimate the size of this potential difference. 
Because the standards for research quality in Registered Reports are at least equal to ordinary peer review, and the statistical power requirements may exceed those in the standard literature [@Maxwell2004; @Szucs2017], such a difference would be unlikely to be due to "failed" studies or false negatives.
Barring large confounfds, such as substantial differences in the prior probability of hypotheses tested in Registered Reports versus the standard literature, a much lower positive result rate in Registered Reports might then indicate that publication bias is not a desirable filter for poorly conducted studies, and that we ought to worry about high-quality negative results we are missing because of it.

@@

The sample size of standard reports was pre-specified to replicate the one used by Fanelli [-@Fanelli2010], $n = 150$, since it matched the maximum number of Registered Reports available at the time ($n = 151$, see below) and piloting indicated that the required coding time would just fit our resource constraints.
Standard reports were selected by searching the 633 journals listed under "Psychiatry/Psychology" in the Essential Science Indicators database for papers published between 2013 and 2018 that contained the phrase "test$^\ast$ the hypothes$^\ast$" in title, abstract, or keywords.
We then randomly selected 150 papers from the 1919 papers that resulted from this search. Excluded papers were replaced by resampling twice (this decision was not preregistered), which led to accidental oversampling and a final sample size of 152 (see Fig.\ \@ref(fig:sampling)).

@@

In Registered Reports, we coded the first *preregistered* hypothesis, thus excluding unregistered pilot studies.
The coding procedure was identical for both article formats in all other respects. 
Coding disagreements between "full" and "partial" support were deemed minor since they would not affect the final results. 
Thus, only disagreements affecting the binary support (full or partial) vs no support classification were treated as major and resolved through discussion.
MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code ($`r sum(included$coded_by_AS & included$is_RR==1)`$ RRs and $`r sum(included$coded_by_AS & included$is_RR==0)`$ SRs). 
Only `r support.disagreement.major` disagreements were major (Cohen's kappa = `r printp(kappa.support)`) and subsequently resolved by discussion; `r support.disagreement.minor` were minor (disagreement between "support" and "partial support"). 
We overturned the preregistered plan that AS would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
Because removing all indicators that could have identified Registered Reports as such from their full texts would have been practically impossible, coding was not blind to publication format (Registered Report vs standard report).

@@

We would accept our hypothesis that Registered Reports have a lower positive result rate than standard reports if the observed difference between Registered Reports and standard reports was significantly smaller than 0 *and* not statistically equivalent to a range from $-6\%$ to $+6\%$ (both at $\alpha = 5\%$)^[Note that these inference criteria are logically equivalent to "significantly smaller than 0 and not statistically equivalent to a range from $-6\%$ to $0\%$": Since the first criterion (statistically smaller than 0) requires the $90\%$ CI to end below 0, half of the equivalence range specified in the second criterion $\,$---$\,$from $0\%$ to $+6\%\,$---$\,$ is redundant (which we failed to notice before preregistering the analysis).]. 
Specifying a smallest effect size of interest of $6\%$ absolute risk reduction provides an initial yardstick to evaluate our results and make our prediction falsifiable.
However, the value of $\pm 6\%$ does not possess an intrinsic theoretical meaning. 
As the emerging meta-psychological literature matures, we hope to see future research base the smallest effect size of interest on increasingly well-informed empirical and theoretical considerations.

@@

## Exploratory analyses
For ease of communication we will refer to papers that were classified as close replications of previously published work as "replications" and to all other studies as "original", even though the latter include some conceptual replications and internal replications (as explained above).
As expected, replications were much more common among Registered Reports ($`r n.rep.RR` / `r n.RR` = `r printnum(prop.rep.RR*100)`\%$) than standard reports ($`r n.rep.SR` / `r n.SR` = `r printnum(prop.rep.SR*100)`\%$), and replication Registered Reports had a descriptively lower positive result rate than original Registered Reports (see Table 1).
However, this finding fails to explain the main result described above:
When analysing only original papers, the difference between the positive result rates of Registered Reports and standard reports, $`r printnum((prop.orig.support.RR-prop.orig.support.SR)*100)`\%$, was still significantly smaller than 0 ($\chi^2(`r origproptest$parameter`) = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(abs(reptost$TOST_z1), abs(reptost$TOST_z2)))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.

@@

## Limitations
Since coders could not be blinded to an article's publication format, their judgment may have been biased.
Our study was not an experiment$\,$---$\,$hypotheses, authors, and editors were not randomly assigned to each publication format$\,$---$\,$and thus precludes strong causal inferences.
As discussed above, it seems highly plausible that Registered Reports reduce publication bias and QRPs, which in turn reduces the positive result rate. 
Yet we neither know exactly how effective Registered Reports are at reducing bias, nor how large the effect on positive results would be in the absence of potential confounds. 
One such confound, as just discussed, could be that Registered Reports may be used for particularly risky hypotheses.
Another confound could be that the format attracts particularly conscientious authors who try to minimise the risk of inflated error rates regardless of the report format they use. 
As a third potential confound, journals that offer Registered Reports may have more progressive editorial policies which aim to reduce publication bias and type-I error inflation for all empirical articles they publish.
This could lead to less bias in the Registered-Reports literature even if the format's safeguards against certain QRPs were actually ineffective. 
Additional research, ideally with prospective and experimental or quasi-experimental study designs, is needed to further investigate the influence of such factors.
However, a cursory look at the three journals which contributed both standard reports and Registered Reports to our dataset (*`r bfjournals[1]`*, *`r bfjournals[2]`*, and *`r bfjournals[3]`*) suggests that the pattern observed in our main analysis may hold for within-journal comparisons, which would speak against a strong influence of an editorial-policy confound:
In these three journals, $`r n.support.SR.bf`/`r n.SR.bf`$ ($`r printnum(prop.support.SR.bf*100)`\%$; $95 \%$ CI [`r printnum(min(SR.binom.bf$conf.int)*100)`, `r printnum(max(SR.binom.bf$conf.int)*100)`]) standard reports had positive results, compared to only $`r n.support.RR.bf`/`r n.RR.bf`$ ($`r printnum(prop.support.RR.bf*100)`\%$; $95 \%$ CI [`r printnum(min(RR.binom.bf$conf.int)*100)`, `r printnum(max(RR.binom.bf$conf.int)*100)`]) Registered Reports.

### 2021-02-18 submission2/positive_results_SRs_RRs_revision1.tex
Updated revised manuscript

Since the 1950s, scientists have repeatedly noted a suspiciously high \enquote{success} rate in Psychology:
Studying 362 empirical articles published in four Psychology journals in 1955/56, Sterling (1959) found that \(97.28\%\) of studies using significance tests rejected the null hypothesis.
A later replication of this study reported \(95.56\%\) statistically significant results in articles from 1986/87 (Sterling, Rosenbaum, \& Weinkam, 1995).
Similarly, a seminal study by Fanelli (2010) compared the literatures of 20 disciplines and found that \(91.5\%\) of papers published in Psychology reported support for their first hypothesis, the highest estimate of all disciplines in the study.
For these percentages to be a realistic representation of the research psychologists conduct, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed \(90\%\).
Put differently, nearly all predictions researchers make must be correct, and either the studied effects or the used samples (given the same design) must consistently be very large.
These two assumptions appear highly implausible a priori, and available evidence on average statistical power in the literature shows that at least one does not hold (e.g., Szucs \& Ioannidis, 2017).

@@

Some have argued that selecting for positive results is defensible\(\,\)---\(\,\)desirable, even\(\,\)---\(\,\)because it weeds out low-quality research that would only pollute the literature (e.g., Cleophas \& Cleophas, 1999).
If most negative results that are currently missing from the literature are indeed due to immature ideas or poor methods, a literature that selects studies based on \emph{quality} instead of results should contain a similar proportion of positive results as the current one.
How many positive and negative results would such an unbiased literature contain in reality?
We investigated this question by comparing the rate of positive results in the Psychology literature to studies published in a new format designed to minimise publication bias and QRPs: Registered Reports.

@@

The goal of our study was to test if Registered Reports in Psychology have a lower positive result rate than articles published in the traditional way (henceforth \enquote{standard reports}, SRs), and to estimate the size of this potential difference.
Because the standards for research quality in Registered Reports are at least equal to ordinary peer review, and the statistical power requirements may exceed those in the standard literature (Maxwell, 2004; Szucs \& Ioannidis, 2017), such a difference would be unlikely to be due to \enquote{failed} studies or false negatives.
Should the positive result rate in Registered Reports be much lower than in the standard literature, it might then indicate that publication bias is not a desirable filter for poorly conducted studies, and that we ought to worry about high-quality negative results we are missing because of it.

@@

The sample size of standard reports was pre-specifided to replicate Fanelli's (2010) (\(n = 150\)) since it matched the maximum number of available Registered Reports (\(n = 151\), see below) and piloting indicated that the required coding time would just fit our resource constraints.
Standard reports were selected by searching the 633 journals listed under \enquote{Psychiatry/Psychology} in the Essential Science Indicators database for papers published between 2013 and 2018 that contained the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} in title, abstract, or keywords.
We then randomly selected 150 papers from the 1919 papers that resulted from this search. Excluded papers were replaced by resampling twice (this decision was not preregistered), which led to accidental oversampling and a final sample size of 152 (see Fig.~\ref{fig:sampling}).

@@

In Registered Reports, we coded the first \emph{preregistered} hypothesis, thus excluding unregistered pilot studies.
Coding disagreements between \enquote{full} and \enquote{partial} support were deemed minor since they would not affect the final results.
Thus, only disagreements affecting the binary support (full or partial) vs no support classification were treated as major and resolved through discussion.
MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code (\(24\) RRs and \(47\) SRs).
Only 3 disagreements were major (Cohen's kappa = .808) and subsequently resolved by discussion; 15 were minor (disagreement between \enquote{support} and \enquote{partial support}).
We overturned the preregistered plan that AS would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
Coders were not blind to condition (Registered Report vs standard report) because access to the full text was often necessary, the content of which would have made most Registered Reports clearly identifiable.

@@

We would accept our hypothesis that Registered Reports have a lower positive result rate than standard reports if the observed difference between Registered Reports and standard reports was significantly smaller than 0 \emph{and} not statistically equivalent to a range from \(-6\%\) to \(+6\%\) (both at \(\alpha = 5\%\)).

@@

For ease of communication we will refer to papers that were classified as close replications of previously published work as \enquote{replications} and to all other studies as \enquote{original}, even though the latter include some conceptual replications and internal replications (as explained above).
As expected, replications were much more common among Registered Reports (\(41 / 71 = 57.75\%\)) than standard reports (\(4 / 152 = 2.63\%\)), and replication Registered Reports had a descriptively lower positive result rate than original Registered Reports (see Table 1).
However, this finding fails to explain the main result described above:
When analysing only original papers, the difference between the positive result rates of Registered Reports and standard reports, \(-45.95\%\), was still significantly different from 0 (\(\chi^2(1) = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).

@@

Our study was not an experiment\(\,\)---\(\,\)hypotheses, authors, and editors were not randomly assigned to each publication format\(\,\)---\(\,\)and thus precludes strong causal inferences.
As discussed above, it seems highly plausible that Registered Reports reduce publication bias and QRPs, which in turn reduces the positive result rate.
Yet we neither know exactly how effective Registered Reports are at reducing bias, nor how large the effect on positive results would be in the absence of potential confounds.
One such confound, as just discussed, could be that Registered Reports may be used for particularly risky hypotheses.
Another confound could be that the format attracts particularly conscientious authors who try to minimise the risk of inflated error rates regardless of the report format they use.
This would lead to less bias in the Registered-Reports literature even if the format's safeguards against certain QRPs were actually ineffective.

@@

\href{https://osf.io/aqr2s/}{Data} and code necessary to reproduce all analyses reported here, as well as the \href{https://osf.io/qw798/}{Appendix}, the \href{https://osf.io/sy927/}{preregistration}, and additional supplementary files, are available at \url{https://osf.io/dbhgr}.
The manuscript, including figures and statistical analyses, the \href{https://osf.io/qw798/}{Appendix}, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).

@@

@@

@@

>>>>

Since the 1950s, scientists have repeatedly noted a suspiciously high \enquote{success} rate in Psychology:
Studying 362 empirical articles published in four Psychology journals in 1955/56, Sterling (1959) found that \(97.28\%\) of studies using significance tests rejected the null hypothesis.
A later replication of this study reported \(95.56\%\) statistically significant results in articles from 1986/87 (Sterling, Rosenbaum, \& Weinkam, 1995).
Similarly, a seminal study by Fanelli (2010) analysed authors' verbal conclusions in hypothesis-testing papers sampled from the literatures of 20 disciplines and found that \(91.5\%\) of papers published in Psychology claimed support for their first hypothesis\(\,\)---\(\,\)the highest estimate of all disciplines in the study.
For these percentages to be a realistic representation of the research psychologists conduct, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed \(90\%\).
Put differently, nearly all predictions researchers make must be correct, and either the studied effects or the used samples (given the same design) must consistently be very large.
These two assumptions appear highly implausible a priori, and available evidence on average statistical power in the literature shows that at least one does not hold (e.g., Szucs \& Ioannidis, 2017).

@@

Some have argued that negative results are often uninformative or the result of low-quality research and should not be published at the same rate as positive results to avoid cluttering the literature (e.g., Cleophas \& Cleophas, 1999; Baumeister, 2016; Mitchell, 2014).
If most negative results that are currently missing from the literature are indeed due to immature ideas or poor methods, a literature that selects studies based on \emph{quality} instead of results should contain a similar proportion of positive results as the current one.
How many positive and negative results would such an unbiased literature contain in reality?
We investigated this question by comparing the rate of positive results in the Psychology literature to studies published in a new format designed to minimise publication bias and QRPs: Registered Reports.

@@

The goal of our study was to test if Registered Reports in Psychology have a lower positive result rate than articles published in the traditional way (henceforth \enquote{standard reports}, SRs), and to estimate the size of this potential difference.
Because the standards for research quality in Registered Reports are at least equal to ordinary peer review, and the statistical power requirements may exceed those in the standard literature (Maxwell, 2004; Szucs \& Ioannidis, 2017), such a difference would be unlikely to be due to \enquote{failed} studies or false negatives.
Barring large confounfds, such as substantial differences in the prior probability of hypotheses tested in Registered Reports versus the standard literature, a much lower positive result rate in Registered Reports might then indicate that publication bias is not a desirable filter for poorly conducted studies, and that we ought to worry about high-quality negative results we are missing because of it.

@@

The sample size of standard reports was pre-specified to replicate the one used by Fanelli (2010), \(n = 150\), since it matched the maximum number of Registered Reports available at the time (\(n = 151\), see below) and piloting indicated that the required coding time would just fit our resource constraints.
Standard reports were selected by searching the 633 journals listed under \enquote{Psychiatry/Psychology} in the Essential Science Indicators database for papers published between 2013 and 2018 that contained the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} in title, abstract, or keywords.
We then randomly selected 150 papers from the 1919 papers that resulted from this search. Excluded papers were replaced by resampling twice (this decision was not preregistered), which led to accidental oversampling and a final sample size of 152 (see Fig.~\ref{fig:sampling}).

@@

In Registered Reports, we coded the first \emph{preregistered} hypothesis, thus excluding unregistered pilot studies.
The coding procedure was identical for both article formats in all other respects.
Coding disagreements between \enquote{full} and \enquote{partial} support were deemed minor since they would not affect the final results.
Thus, only disagreements affecting the binary support (full or partial) vs no support classification were treated as major and resolved through discussion.
MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code (\(24\) RRs and \(47\) SRs).
Only 3 disagreements were major (Cohen's kappa = .808) and subsequently resolved by discussion; 15 were minor (disagreement between \enquote{support} and \enquote{partial support}).
We overturned the preregistered plan that AS would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
Because removing all indicators that could have identified Registered Reports as such from their full texts would have been practically impossible, coding was not blind to publication format (Registered Report vs standard report).

@@

We would accept our hypothesis that Registered Reports have a lower positive result rate than standard reports if the observed difference between Registered Reports and standard reports was significantly smaller than 0 \emph{and} not statistically equivalent to a range from \(-6\%\) to \(+6\%\) (both at \(\alpha = 5\%\))\footnote{Note that these inference criteria are logically equivalent to \enquote{significantly smaller than 0 and not statistically equivalent to a range from \(-6\%\) to \(0\%\)}: Since the first criterion (statistically smaller than 0) requires the \(90\%\) CI to end below 0, half of the equivalence range specified in the second criterion \(\,\)---\(\,\)from \(0\%\) to \(+6\%\,\)---\(\,\) is redundant (which we failed to notice before preregistering the analysis).}.
Specifying a smallest effect size of interest of \(6\%\) absolute risk reduction provides an initial yardstick to evaluate our results and make our prediction falsifiable.
However, the value of \(\pm 6\%\) does not possess an intrinsic theoretical meaning.
As the emerging meta-psychological literature matures, we hope to see future research base the smallest effect size of interest on increasingly well-informed empirical and theoretical considerations.

@@

For ease of communication we will refer to papers that were classified as close replications of previously published work as \enquote{replications} and to all other studies as \enquote{original}, even though the latter include some conceptual replications and internal replications (as explained above).
As expected, replications were much more common among Registered Reports (\(41 / 71 = 57.75\%\)) than standard reports (\(4 / 152 = 2.63\%\)), and replication Registered Reports had a descriptively lower positive result rate than original Registered Reports (see Table 1).
However, this finding fails to explain the main result described above:
When analysing only original papers, the difference between the positive result rates of Registered Reports and standard reports, \(-45.95\%\), was still significantly smaller than 0 (\(\chi^2(1) = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).

@@

Since coders could not be blinded to an article's publication format, their judgment may have been biased.
Our study was not an experiment\(\,\)---\(\,\)hypotheses, authors, and editors were not randomly assigned to each publication format\(\,\)---\(\,\)and thus precludes strong causal inferences.
As discussed above, it seems highly plausible that Registered Reports reduce publication bias and QRPs, which in turn reduces the positive result rate.
Yet we neither know exactly how effective Registered Reports are at reducing bias, nor how large the effect on positive results would be in the absence of potential confounds.
One such confound, as just discussed, could be that Registered Reports may be used for particularly risky hypotheses.
Another confound could be that the format attracts particularly conscientious authors who try to minimise the risk of inflated error rates regardless of the report format they use.
As a third potential confound, journals that offer Registered Reports may have more progressive editorial policies which aim to reduce publication bias and type-I error inflation for all empirical articles they publish.
This could lead to less bias in the Registered-Reports literature even if the format's safeguards against certain QRPs were actually ineffective.
Additional research, ideally with prospective and experimental or quasi-experimental study designs, is needed to further investigate the influence of such factors.
However, a cursory look at the three journals which contributed both standard reports and Registered Reports to our dataset (\emph{Attention, Perception, and Psychophysics}, \emph{Cognition and Emotion}, and \emph{Frontiers in Psychology}) suggests that the pattern observed in our main analysis may hold for within-journal comparisons, which would speak against a strong influence of an editorial-policy confound:
In these three journals, \(11/13\) (\(84.62\%\); \(95 \%\) CI {[}54.55, 98.08{]}) standard reports had positive results, compared to only \(7/14\) (\(50.00\%\); \(95 \%\) CI {[}23.04, 76.96{]}) Registered Reports.

@@

\href{https://osf.io/aqr2s/}{Data} and code necessary to reproduce all analyses reported here, as well as the \href{https://osf.io/qw798/}{Appendix}, the \href{https://osf.io/sy927/}{preregistration}, and additional supplementary files, are available at \url{https://osf.io/dbhgr}.
The manuscript, including figures and statistical analyses, the \href{https://osf.io/qw798/}{Appendix}, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).

@@

\leavevmode\hypertarget{ref-Baumeister2016}{}%
Baumeister, R. F. (2016). Charting the future of social psychology on stormy seas: Winners, losers, and recommendations. \emph{Journal of Experimental Social Psychology}, \emph{66}, 153--158. \url{https://doi.org/10.1016/j.jesp.2016.02.003}

@@

\leavevmode\hypertarget{ref-Mitchell2014}{}%
Mitchell, J. (2014). On the evidentiary emptiness of failed replications.

@@

\leavevmode\hypertarget{ref-R-tidyr}{}%
Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
